Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-04-22 ms/main.tex
Fix illustration fig ref

Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\dot{p}$.
Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
\begin{equation}\label{eq:horizontal}
\begin{aligned}
\hat{p} \;=
\dot{p} [v + (1-v)p] + (1-\dot{p}) [(1-v)p] \;= 
v \dot{p} + (1-v) p \;.
\end{aligned}
\end{equation}
Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$ (i.e. donation game). \autoref{fig:illustration}d shows the payoff matrix: the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.

@@

It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}c).

@@

The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}b).

@@

The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection. Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}d), which depends on the phenotypes of the two interaction partners.

@@

where fitness values are taken from \autoref{fig:illustration}d and \autoref{table:interactions}, and the population mean fitness is

>>>>

Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\dot{p}$.
Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
\begin{equation}\label{eq:horizontal}
\begin{aligned}
\hat{p} \;=
\dot{p} [v + (1-v)p] + (1-\dot{p}) [(1-v)p] \;= 
v \dot{p} + (1-v) p \;.
\end{aligned}
\end{equation}
Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$ (i.e. donation game). \autoref{fig:illustration}c shows the payoff matrix: the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.

@@

It occurs between socially interacting partners with probability~$\alpha$, or between a random pair with probability~$1-\alpha$ (see~\autoref{fig:illustration}b).

@@

The probability of successful horizontal transmission of phenotypes $A$ and $B$ are $T_A$ and $T_B$, respectively (\autoref{table:interactions}, \autoref{fig:illustration}d).

@@

The frequency of $A$ among parents follows a similar dynamic but must also include the effect of natural selection. Therefore, each right-hand term from \autoref{eq:nextgen_adults} is multiplied by the corresponding fitness value (\autoref{table:interactions}, \autoref{fig:illustration}c), which depends on the phenotypes of the two interaction partners.

@@

where fitness values are taken from \autoref{fig:illustration}c and \autoref{table:interactions}, and the population mean fitness is
